Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-26 paper/paper.tex
updated table 3

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Name}} &
    \#~Option Cand. &
    \#~Plausible Rules &    
    \multicolumn{1}{c}{Rank} \\

     &
    \multicolumn{1}{c}{(step 1)} &
    \multicolumn{1}{c}{(step 2)} &    
    \multicolumn{1}{c}{(step 3)} \\

    \midrule
    Ping Scan & 5 & 2 & - \\
    SYN Flood & 2 & 2 & - \\
    JBoss JMX & 23 & 381 & 23 \\
    %%   WeBid & 23 & - & -\\    
    ColdFusion & 19 & 39 & 5\\
    .htaccess access & 17 & 2,458 & 2\\
    .idq access & 19 & 1,111 & 2 \\
    iisadmin access & 17 & 861 & 1 \\
    /system32/ in URI & 20 & 3,665 & 2 \\
    Script tag in URI & 22 & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Name}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\# Variants}} &
    \#~Option Cand. &
    \#~Plausible Rules &    
    \multicolumn{1}{c}{Rank} \\

     &
    \multicolumn{1}{c}{} &
    \multicolumn{1}{c}{(step 1)} &
    \multicolumn{1}{c}{(step 2)} &    
    \multicolumn{1}{c}{(step 3)} \\

    \midrule
    Ping Scan & 5 & 5 & 2 & - \\
    SYN Flood & 3 & 2 & 2 & - \\
    JBoss JMX & 4 & 23 & 381 & 23 \\
    %%   WeBid & - & 23 & - & -\\    
    ColdFusion & 6 & 19 & 39 & 5\\
    .htaccess access & 4 & 17 & 2,458 & 2\\
    .idq access & 13 & 19 & 1,111 & 2 \\
    iisadmin access & 3 & 17 & 861 & 1 \\
    /system32/ in URI & 3 & 20 & 3,665 & 2 \\
    Script tag in URI & 22 & 22 & - & - \\
    \bottomrule
  \end{tabular}
\end{table}
